---
title: "Symptomatic Infection and Severe Outcomes among Children from 6-11 years"
author: "CIDACS-Fiocruz"
date: "4/13/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(knitr)
library(magrittr)
library(tidyverse)
library(magrittr)
library(tidytable)
library(lubridate)
knitr::opts_chunk$set(echo = FALSE)

cv = readRDS("/.rds")


## Relevel vaccine status (the reference here must me be unvaccinated individuals - uv)

cv$status_vacinal=as.factor(cv$status_vacinal)
cv$status_vacinal=relevel(cv$status_vacinal,ref="uv")

cv$status_waning=as.factor(cv$status_waning)
cv$status_waning=relevel(cv$status_waning,ref="uv")


##Converting all variables from our model to categorical  
##For analysis model all variables included must be categorical 

cv$uf=as.factor(cv$uf) 
cv$uf=relevel(cv$uf,ref="35")
cv$mes = as.factor(cv$mes)
cv$idade=as.factor(cv$idade)
cv$confirmado = as.factor(cv$confirmado)
cv$q_measure_1f_12 = as.factor(cv$q_measure_1f_12)
cv$prev_infect=as.factor(cv$prev_infect) 
cv$prev_infect=relevel(cv$prev_infect,ref="Not previous infected")
cv$nome_grande_regiao=as.factor(cv$nome_grande_regiao)
cv$SE = as.factor(cv$SE)

```

## Tabela Demográfica da população entre 6-11 anos. 

```{r echo=FALSE, results='asis'}

library(gtsummary)

cv_v1 = cv %>% select(id_vigvac,confirmado,idade,sexo,raca,
                       q_measure_1f_12,nome_grande_regiao,outcome,n_comorb, prev_infect, mes, hosp_event, death_event, uf)
cv_all_char = cv_v1 %>% tbl_summary(by = confirmado, include = -id_vigvac,digits = all_categorical() ~ c(0, 1))

print(cv_all_char)


```

## Tabela dos testes positivos e negativos 
Estratificados por status vacinal e por tempo após primeira e segunda dose. 

```{r echo=FALSE, results='asis'}

library(knitr)
library(gtsummary)

#Table Characteristic for the omicron group 
cv_v1 = cv %>% select(id_vigvac,confirmado, status_vacinal, death_event, hosp_event, UTI_2)
cv_char = cv_v1 %>% tbl_summary(by = confirmado, include = -id_vigvac, percent = "row",digits = all_categorical() ~ c(0, 2))

print(cv_char)


```

## Symptomatic Infection - Children - 6-11 years - Status Vacinal
### ODDS RATIO and VE:Crude Model
```{r echo=FALSE, results='asis'}
library(knitr)
library(parameters)


#Model for Symptomatic infection

##Odd Ration - crude
cv_crude = glm(confirmado == "Confirmado" ~ status_vacinal,
               family = binomial, data = cv)
cv_crude_results = model_parameters(
  cv_crude, exponentiate = T, ci_method="wald")

VE = (1-cv_crude_results$Coefficient)*100
high = (1-cv_crude_results$CI_low)*100
low = (1-cv_crude_results$CI_high)*100

cv_crude_results$VE= VE
cv_crude_results$high = high
cv_crude_results$low = low

kable(cv_crude_results[1:5,], caption = "Odds Ratio - Crude - Symptomatic Infection",digits = 2)


```

## Symptomatic Infection - Status Vacinal 
### ODDS RATIO and VE:Adjusted Model
```{r echo=FALSE, results='asis'}
library(knitr)
library(parameters)
library(logistf)

##Odd Ratio - Adjusted 

cv_adj = glm(confirmado == "Confirmado" ~ status_vacinal+mes+raca+n_comorb+q_measure_1f_12+nome_grande_regiao+prev_infect,family = binomial, data = cv)

cv_adj_results = model_parameters(
  cv_adj, exponentiate = T, ci_method="wald") 

VE = (1-cv_adj_results$Coefficient)*100
high = (1-cv_adj_results$CI_low)*100
low = (1-cv_adj_results$CI_high)*100

cv_adj_results$VE= VE
cv_adj_results$high = high
cv_adj_results$low = low

kable(cv_adj_results[1:12,], caption = "Odds Ratio - glm adjust - Symptomatic Infection", digits = 2)

##Adjusted - logistf

fit_adj = logistf(data=cv, confirmado == "Confirmado" ~ status_vacinal+mes+sexo+idade+n_comorb+nome_grande_regiao+prev_infect, firth=TRUE, pl=TRUE, method = "Penalized ML", method.ci ="profile likelihood")
fit_adj_results = model_parameters(fit_adj, exponentiate = T, ci_method = "profile",  digits = 2)

VE = (1-fit_adj_results$Coefficient)*100
high = (1-fit_adj_results$CI_low)*100
low = (1-fit_adj_results$CI_high)*100

fit_adj_results$VE= VE
fit_adj_results$high = high
fit_adj_results$low = low

kable(fit_adj_results[1:12,], caption = "Odds Ratio - Fit Adjust - Symptomatic Infection", digits = 2, format.args = list(scientific = FALSE))


```

## Tabela dos testes positivos e negativos 
Hospitalisation or death events

```{r echo=FALSE, results='asis'}

library(knitr)
library(gtsummary)
#Severe outcomes 
omic_neg = cv %>% filter(confirmado == "Negativo")
omic_posit = cv %>% filter(confirmado=="Confirmado" & outcome == "Hosp_Death")
omicsev=bind_rows.(omic_neg,omic_posit)

#Table Characteristic for the omicron group 
cv_v1 = omicsev %>% select(id_vigvac,confirmado, status_vacinal)
cv_char = cv_v1 %>% tbl_summary(by = confirmado, include = -id_vigvac, percent = "row",digits = all_categorical() ~ c(0, 2))

print(cv_char)

```


## Omicron period - Severe outcomes (hospitalisation or death)  
### ODDS RATIO + VE 

```{r echo=FALSE, results='asis'}
library(knitr)
library(parameters)

#Severe outcomes 
omic_neg = cv %>% filter(confirmado == "Negativo")
omic_posit = cv %>% filter(confirmado=="Confirmado" & outcome == "Hosp_Death")
omicsev=bind_rows.(omic_neg,omic_posit)


##Odd Ratio - crude
omicsev_crude = glm(confirmado == "Confirmado" ~ status_vacinal,
                 family = binomial, data = omicsev)
omicsev_crude_results = model_parameters(
  omicsev_crude, exponentiate = T, ci_method="wald")

VE = (1-omicsev_crude_results$Coefficient)*100
high = (1-omicsev_crude_results$CI_low)*100
low = (1-omicsev_crude_results$CI_high)*100

omicsev_crude_results$VE = VE
omicsev_crude_results$high = high
omicsev_crude_results$low = low

kable(omicsev_crude_results[1:5,], caption = "Odds Ratio - Crude - Hospitalisation or Death - Omicron", digits = 2,format.args = list(scientific = FALSE))

##Adjusted - glm 
omicsev_adj = glm(confirmado == "Confirmado"~status_vacinal+mes+raca+n_comorb+q_measure_1f_12+nome_grande_regiao+prev_infect,family = binomial, data = omicsev)

omicsev_adj_results = model_parameters(
  omicsev_adj, exponentiate = T, ci_method="profile") 

VE = (1-omicsev_adj_results$Coefficient)*100
high = (1-omicsev_adj_results$CI_low)*100
low = (1-omicsev_adj_results$CI_high)*100

omicsev_adj_results$VE= VE
omicsev_adj_results$high = high
omicsev_adj_results$low = low

kable(omicsev_adj_results[1:12,], caption = "Odds Ratio - glm adjust - Hospitalisation or Death", digits = 2)


```

## Tabela dos testes positivos e negativos 
Only Hospitalisation

```{r echo=FALSE, results='asis'}

library(knitr)
library(gtsummary)

#Hospitalisation 
omic_neg = cv %>% filter(confirmado == "Negativo")
omic_hosp = cv %>% filter(confirmado=="Confirmado" & hosp_event == "Hospitalization")
omicsev=bind_rows.(omic_neg,omic_hosp)


#Table Characteristic for the omicron group 
cv_v1 = omicsev %>% select(id_vigvac,confirmado, status_vacinal)
cv_char = cv_v1 %>% tbl_summary(by = confirmado, include = -id_vigvac, percent = "row",digits = all_categorical() ~ c(0, 2))

print(cv_char)

```

## Omicron period - Severe outcomes (hospitalisation) + Status Vacinal + Mês 
### ODDS RATIO + VE 

```{r echo=FALSE, results='asis'}
library(knitr)
library(parameters)
library(logistf)

#Hospitalisation
omic_neg = cv %>% filter(confirmado == "Negativo")
omic_hosp = cv %>% filter(confirmado=="Confirmado" & hosp_event == "Hospitalization")
omicsev=bind_rows.(omic_neg,omic_hosp)


##Odd Ratio - crude
omicsev_crude = glm(confirmado == "Confirmado" ~ status_vacinal,
                 family = binomial, data = omicsev)
omicsev_crude_results = model_parameters(
  omicsev_crude, exponentiate = T, ci_method="wald")

VE = (1-omicsev_crude_results$Coefficient)*100
high = (1-omicsev_crude_results$CI_low)*100
low = (1-omicsev_crude_results$CI_high)*100

omicsev_crude_results$VE = VE
omicsev_crude_results$high = high
omicsev_crude_results$low = low

kable(omicsev_crude_results[1:5,], caption = "Odds Ratio - Crude - Severe Outcomes - Omicron", digits = 2,format.args = list(scientific = FALSE))

##Adjusted - glm + profile CI method 

omicsev_adj = glm(confirmado == "Confirmado"~status_vacinal+mes+raca+n_comorb+q_measure_1f_12+nome_grande_regiao+prev_infect,family = binomial, data = omicsev)

omicsev_adj_results = model_parameters(
  omicsev_adj, exponentiate = T, ci_method="profile") 

VE = (1-omicsev_adj_results$Coefficient)*100
high = (1-omicsev_adj_results$CI_low)*100
low = (1-omicsev_adj_results$CI_high)*100

omicsev_adj_results$VE= VE
omicsev_adj_results$high = high
omicsev_adj_results$low = low

kable(omicsev_adj_results[1:12,], caption = "Odds Ratio - glm Adjust - Hospitalisation", digits = 2)

##Adjusted - logistf

fitsev_adj = logistf(data=omicsev, confirmado == "Confirmado" ~ status_vacinal+mes+sexo+idade+n_comorb+nome_grande_regiao+prev_infect, firth=TRUE, pl=TRUE, method = "Penalized ML", method.ci ="profile likelihood")
fitsev_adj_results = model_parameters(fitsev_adj, exponentiate = T, ci_method = "profile",  digits = 2)

VE = (1-fitsev_adj_results$Coefficient)*100
high = (1-fitsev_adj_results$CI_low)*100
low = (1-fitsev_adj_results$CI_high)*100

fitsev_adj_results$VE= VE
fitsev_adj_results$high = high
fitsev_adj_results$low = low

kable(fitsev_adj_results[1:12,], caption = "Odds Ratio - Fit Adjust - Hospitalisation", digits = 2, format.args = list(scientific = FALSE))


```

Tabela positivos e negativos ICU
```{r echo=FALSE, results='asis'}

library(knitr)
library(gtsummary)
#Severe outcomes 
omic_neg = cv %>% filter(confirmado == "Negativo")
omic_uti = cv %>% filter(confirmado=="Confirmado" & UTI_2 == "1")
omicsev=bind_rows.(omic_neg,omic_uti)


#Table Characteristic for the omicron group 
cv_v1 = omicsev %>% select(id_vigvac,confirmado, status_vacinal)
cv_char = cv_v1 %>% tbl_summary(by = confirmado, include = -id_vigvac, percent = "row",digits = all_categorical() ~ c(0, 2))

print(cv_char)

```

## Omicron period - Severe outcomes (ICU) + Status Vacinal + Mês 
### ODDS RATIO + VE 

```{r echo=FALSE, results='asis'}
library(knitr)
library(parameters)
library(logistf)


#Severe outcomes 
omic_neg = cv %>% filter(confirmado == "Negativo")
omic_uti = cv %>% filter(confirmado=="Confirmado" & UTI_2 == "1")
omicsev=bind_rows.(omic_neg,omic_uti)


##Odd Ratio - crude
omicsev_crude = glm(confirmado == "Confirmado" ~ status_vacinal,
                 family = binomial, data = omicsev)
omicsev_crude_results = model_parameters(
  omicsev_crude, exponentiate = T, ci_method="wald")

VE = (1-omicsev_crude_results$Coefficient)*100
high = (1-omicsev_crude_results$CI_low)*100
low = (1-omicsev_crude_results$CI_high)*100

omicsev_crude_results$VE = VE
omicsev_crude_results$high = high
omicsev_crude_results$low = low

kable(omicsev_crude_results[1:5,], caption = "Odds Ratio - Crude - ICU admission", digits = 2,format.args = list(scientific = FALSE))

##Adjusted - glm 
omicsev_adj = glm(confirmado == "Confirmado"~status_vacinal+mes+raca+n_comorb+q_measure_1f_12+nome_grande_regiao+prev_infect,family = binomial, data = omicsev)

omicsev_adj_results = model_parameters(
  omicsev_adj, exponentiate = T, ci_method="profile") 

VE = (1-omicsev_adj_results$Coefficient)*100
high = (1-omicsev_adj_results$CI_low)*100
low = (1-omicsev_adj_results$CI_high)*100

omicsev_adj_results$VE= VE
omicsev_adj_results$high = high
omicsev_adj_results$low = low

kable(omicsev_adj_results[1:12,], caption = "Odds Ratio - glm Adjust - ICU admission", digits = 2)


##Adjusted - logistf

fitsev_adj = logistf(data=omicsev, confirmado == "Confirmado" ~ status_vacinal+mes+sexo+idade+n_comorb+nome_grande_regiao+prev_infect, firth=TRUE, pl=TRUE, method = "Penalized ML", method.ci ="profile likelihood")
fitsev_adj_results = model_parameters(fitsev_adj, exponentiate = T, ci_method = "profile",  digits = 2)

VE = (1-fitsev_adj_results$Coefficient)*100
high = (1-fitsev_adj_results$CI_low)*100
low = (1-fitsev_adj_results$CI_high)*100

fitsev_adj_results$VE= VE
fitsev_adj_results$high = high
fitsev_adj_results$low = low

kable(fitsev_adj_results[1:12,], caption = "Odds Ratio - Fit Adjusted - ICU admission", digits = 2, format.args = list(scientific = FALSE))


```

Tabela positivos e negativos (Death events)
```{r echo=FALSE, results='asis'}

library(knitr)
library(gtsummary)
#Severe outcomes 

omic_neg = cv %>% filter(confirmado == "Negativo")
omic_death= cv %>% filter(confirmado=="Confirmado" & death_event == "Death-related")
omicsev=bind_rows.(omic_neg,omic_death)


#Table Characteristic for the omicron group 
cv_v1 = omicsev %>% select(id_vigvac,confirmado, status_vacinal)
cv_char = cv_v1 %>% tbl_summary(by = confirmado, include = -id_vigvac, percent = "row",digits = all_categorical() ~ c(0, 2))

print(cv_char)

```
## Omicron period - Severe outcomes (Death) + Status Vacinal + Mês 
### ODDS RATIO + VE 

```{r echo=FALSE, results='asis'}
library(knitr)
library(parameters)
library(logistf)

#Severe outcomes 
omic_neg = cv %>% filter(confirmado == "Negativo")
omic_death= cv %>% filter(confirmado=="Confirmado" & death_event == "Death-related")
omicsev=bind_rows.(omic_neg,omic_death)


##Odd Ratio - crude
omicsev_crude = glm(confirmado == "Confirmado" ~ status_vacinal,
                 family = binomial, data = omicsev)
omicsev_crude_results = model_parameters(
  omicsev_crude, exponentiate = T, ci_method="wald")

VE = (1-omicsev_crude_results$Coefficient)*100
high = (1-omicsev_crude_results$CI_low)*100
low = (1-omicsev_crude_results$CI_high)*100

omicsev_crude_results$VE = VE
omicsev_crude_results$high = high
omicsev_crude_results$low = low

kable(omicsev_crude_results[1:5,], caption = "Odds Ratio - Crude - Death", digits = 2,format.args = list(scientific = FALSE))

##Adjusted - logistf

fitsev_adj = logistf(data=omicsev, confirmado == "Confirmado" ~ status_vacinal+mes+sexo+idade+n_comorb+nome_grande_regiao+prev_infect, firth=TRUE, pl=TRUE, method = "Penalized ML", method.ci ="profile likelihood")
fitsev_adj_results = model_parameters(fitsev_adj, exponentiate = T, ci_method = "profile",  digits = 2)

VE = (1-fitsev_adj_results$Coefficient)*100
high = (1-fitsev_adj_results$CI_low)*100
low = (1-fitsev_adj_results$CI_high)*100

fitsev_adj_results$VE= VE
fitsev_adj_results$high = high
fitsev_adj_results$low = low

kable(fitsev_adj_results[1:12,], caption = "Odds Ratio - Fit Adjust - Death", digits = 2, format.args = list(scientific = FALSE))


```

##Multiple Imputation

pacman::p_load(tidyverse,mice)

tnd = readRDS("/.rds")


tnd1 <- tnd  %>%  select(idade,sexo,raca,confirmado,codmun6,uf,nome_grande_regiao,tipo_teste,diabetes:puerpera,status_vacinal,mes,prev_infect, q_measure_1f_12)
tnd1 <- tnd1 %>%  mutate(raca=case_when(
  raca=="(Missing)" ~ NA_character_,
  TRUE ~ as.character(raca)),
                       across(where(is.character),as.factor)
                       )

tnd <- tnd  %>%  mutate(filter_imp=if_else((outcome=="Hosp_Death" & confirmado=="Confirmado") | confirmado=="Negativo",TRUE,FALSE))
imp <- mice(tnd1, maxit=0)
predM <- imp$predictorMatrix
meth <- imp$method
#md.pattern(tnd1)
imp2 <- parlmice(tnd1, maxit = 10, 
             predictorMatrix = predM, 
             method = meth, print =  FALSE, cluster.seed = 07062022,  n.core=2, n.imp.core = 5)
long <- complete(imp2, action='long', include=TRUE)
# Generate new variable
long <- long  %>%  mutate_rowwise.(n_comorb=sum(c_across.(diabetes:drc)))

long <- long %>%  mutate.(n_comorb=as.factor(case_when.(
  n_comorb>=2 ~ "2+",
  TRUE ~ as.character(n_comorb)
))) 
n_comorb=fct_lump(factor(n_comorb),n=2,other_level ="2+")


# Convert back to Mids
imput.short <- as.mids(long)

imp_severe <- filter(imput.short,tnd$filter_imp)
modelo2imp <- with(imput.short,glm(confirmado=="Confirmado"~as.factor(idade)+sexo+raca+status_vacinal+as.factor(mes)+relevel(factor(prev_infect),"Not previous infected")+n_comorb+as.factor(nome_grande_regiao)+as.factor(q_measure_1f_12),family=binomial))
modelo3imp <- with(imp_severe,glm(confirmado=="Confirmado"~as.factor(idade)+sexo+raca+status_vacinal+as.factor(mes)+relevel(factor(prev_infect),"Not previous infected")+n_comorb+as.factor(nome_grande_regiao)+as.factor(q_measure_1f_12),family=binomial))


dt1 <- broom::tidy(pool(modelo3imp),conf.int=T,exponentiate = TRUE) 
dt2 <- broom::tidy(pool(modelo2imp),conf.int=T,exponentiate = TRUE) 

saveRDS(dt2,".rds")
saveRDS(dt1,".rds")



```{r echo=FALSE, results='asis'}
#library(knitr)
#library(parameters)

#delta_MI = readRDS("/.rds")

#delta_MI = delta_MI[,1:7] 


#VE = (1-delta_MI$estimate)*100
#high = (1-delta_MI$conf.low)*100
#low = (1-delta_MI$conf.high)*100

#delta_MI$VE= VE
#delta_MI$high = high
#delta_MI$low = low

#kable(delta_MI[1:80,], caption = "Multiple Imputation - Adjusted - SYMPTOMATIC INFECTION - OMICRON, digits = 2")

```

```{r echo=FALSE, results='asis'}
#library(knitr)
#library(parameters)

#delta_MI = readRDS("/.rds")

#delta_MI = delta_MI[,1:7] 


#VE = (1-delta_MI$estimate)*100
#high = (1-delta_MI$conf.low)*100
#low = (1-delta_MI$conf.high)*100

#delta_MI$VE= VE
#delta_MI$high = high
#delta_MI$low = low

#kable(delta_MI[1:80,], caption = "Multiple Imputation - Adjusted - SEVERE OUCOMES - OMICRON", digits = 2)

```





