---
title: "Symptomatic Infection and Severe Outcomes among Children from 6-11 years"
author: "CIDACS-Fiocruz"
date: "4/13/2022"
output: html_document
---

## The analysis by  


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

## Teste de sensibilidade 



library(knitr)
library(magrittr)
library(tidyverse)
library(magrittr)
library(tidytable)
library(lubridate)
knitr::opts_chunk$set(echo = FALSE)

cv = readRDS("/.rds")

## Relevel vaccine status (the reference here must me be unvaccinated individuals - uv)


cv$status_vacinal=as.factor(cv$status_vacinal)
cv$status_vacinal=relevel(cv$status_vacinal,ref="uv")

##Converting all variables from our model to categorical  
##For analysis model all variables included must be categorical 


cv$idade=as.factor(cv$idade)
cv$confirmado = as.factor(cv$confirmado)
cv$q_measure_1f_12 = as.factor(cv$q_measure_1f_12)
cv$prev_infect=as.factor(cv$prev_infect) 
cv$prev_infect=relevel(cv$prev_infect,ref="Not previous infected")
cv$mes=as.factor(cv$mes)
cv$nome_grande_regiao=as.factor(cv$nome_grande_regiao)



```


## Tabela Demográfica da população entre 6-11 anos. 

```{r echo=FALSE, results='asis'}

library(gtsummary)

cv_v1 = cv %>% select(id_vigvac,confirmado,idade,sexo,raca,
                       q_measure_1f_12,nome_grande_regiao,outcome,n_comorb, prev_infect, mes)
cv_all_char = cv_v1 %>% tbl_summary(by = confirmado, include = -id_vigvac,digits = all_categorical() ~ c(0, 1))

print(cv_all_char)


```

## Tabela dos testes positivos e negativos 
Estratificados por status vacinal e por tempo após primeira e segunda dose. 

```{r echo=FALSE, results='asis'}

library(knitr)
library(gtsummary)

#Table Characteristic for the omicron group 
cv_v1 = cv %>% select(id_vigvac,confirmado, status_vacinal)
cv_char = cv_v1 %>% tbl_summary(by = confirmado, include = -id_vigvac, percent = "row",digits = all_categorical() ~ c(0, 2))

print(cv_char)

```

## Symptomatic Infection - Children - 6-11 years
### ODDS RATIO and VE:  
### Crude Model
```{r echo=FALSE, results='asis'}
library(knitr)
library(parameters)


#Model for Symptomatic infection

##Odd Ration - crude
cv_crude = glm(confirmado == "Confirmado" ~ status_vacinal,
               family = binomial, data = cv)
cv_crude_results = model_parameters(
  cv_crude, exponentiate = T, ci_method="wald")

VE = (1-cv_crude_results$Coefficient)*100
high = (1-cv_crude_results$CI_low)*100
low = (1-cv_crude_results$CI_high)*100

cv_crude_results$VE= VE
cv_crude_results$high = high
cv_crude_results$low = low

kable(cv_crude_results[1:8,], caption = "Odds Ratio - Crude - Symptomatic Infection - Childrens 6-11 anos",digits = 2)


```

### Adjusted model
```{r echo=FALSE, results='asis'}
library(knitr)
library(parameters)
library(logistf)


##Odd Ratio - Adjusted 

cv_adj = glm(confirmado == "Confirmado"~status_vacinal+mes+idade+raca+q_measure_1f_12+n_comorb+prev_infect+nome_grande_regiao,family = binomial, data = cv)

cv_adj_results = model_parameters(
  cv_adj, exponentiate = T, ci_method="wald") 

VE = (1-cv_adj_results$Coefficient)*100
high = (1-cv_adj_results$CI_low)*100
low = (1-cv_adj_results$CI_high)*100

cv_adj_results$VE= VE
cv_adj_results$high = high
cv_adj_results$low = low

kable(cv_adj_results[1:20,], caption = "Odds Ratio - adjusted model- Symptomatic Infection - Children 6-11 years", digits = 2)




```



## Omicron period - Severe outcomes (hospitalisation or death)
### ODDS RATIO

```{r echo=FALSE, results='asis'}
library(knitr)
library(parameters)
library(logistf)

#Severe outcomes 
omic_neg = cv %>% filter(confirmado == "Negativo")
omic_posit = cv %>% filter(confirmado=="Confirmado" & outcome == "Hosp_Death")
omicsev=bind_rows.(omic_neg,omic_posit)


##Odd Ratio - crude
omicsev_crude = glm(confirmado == "Confirmado" ~ status_vacinal,
                 family = binomial, data = omicsev)
omicsev_crude_results = model_parameters(
  omicsev_crude, exponentiate = T, ci_method="wald")

VE = (1-omicsev_crude_results$Coefficient)*100
high = (1-omicsev_crude_results$CI_low)*100
low = (1-omicsev_crude_results$CI_high)*100

omicsev_crude_results$VE= VE
omicsev_crude_results$high = high
omicsev_crude_results$low = low

kable(omicsev_crude_results[1:6,], caption = "Odds Ratio - Crude - Severe Outcomes - Omicron", digits = 2,format.args = list(scientific = FALSE))



##Odd Ratio - Adjusted 
omicsev_adj = logistf(data=omicsev, confirmado == "Confirmado" ~ status_waning+mes+sexo+idade+n_comorb+prev_infect+nome_grande_regiao,
                  firth=TRUE, pl=TRUE, method = "Penalized ML", method.ci ="profile likelihood")


omicsev_adj_results = model_parameters(fitsev, exponentiate = T, ci_method = "profile",  digits = 2)


VE = (1-omicsev_adj_results$Coefficient)*100
high = (1-omicsev_adj_results$CI_low)*100
low = (1-omicsev_adj_results$CI_high)*100

omicsev_adj_results$VE= VE
omicsev_adj_results$high = high
omicsev_adj_results$low = low


kable(omicsev_adj_results[1:6,], caption = "Odds Ratio - Adjusted - Severe Outcomes - Omicron", digits = 2, format.args = list(scientific = FALSE))



```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
