---
title: "VE analysis among adolescent 11-17 years"
author: "CIDACS-Fiocruz"
date: "3/23/2022"
output: html_document
---
## The analysis

```{r setup, include=FALSE}
library(knitr)
library(magrittr)
library(tidyverse)
library(magrittr)
library(tidytable)
knitr::opts_chunk$set(echo = FALSE)

bnt = readRDS(".rds")

## Relevel vaccine status (the reference here must me be unvaccinated individuals - uv)

bnt$status_waning=as.factor(bnt$status_waning)
bnt$status_waning=relevel(bnt$status_waning,ref="uv")


##Converting all variables from our model to categorical  
##For analysis model all variables included must be categorical 

bnt$sexo=as.factor(bnt$sexo)
bnt$idade=as.factor(bnt$idade)
bnt$confirmado = as.factor(bnt$confirmado)
bnt$q_measure_1f_12 = as.factor(bnt$q_measure_1f_12)
bnt$prev_infect=as.factor(bnt$prev_infect) 
bnt$prev_infect=relevel(bnt$prev_infect,ref="Not previous infected")
bnt$SE=as.factor(bnt$SE) 
bnt$nome_grande_regiao=as.factor(bnt$nome_grande_regiao)
bnt$gestante = as.factor(bnt$gestante)
bnt$puerpera = as.factor(bnt$puerpera)
bnt$hosp_event = as.factor(bnt$hosp_event)
bnt$death_event = as.factor(bnt$death_event)


```


## Omicron and delta period
### Table of characteristic:


```{r echo=FALSE, results='asis'}

library(gtsummary)

bnt_v1 = bnt %>% select(id_vigvac,confirmado,status_waning,idade,sexo,raca,
                       q_measure_1f_12,nome_grande_regiao,outcome,n_comorb, prev_infect, gestante, puerpera, hosp_event,death_event)
bnt_all_char = bnt_v1 %>% tbl_summary(by = confirmado, include = -id_vigvac,digits = all_categorical() ~ c(0, 1))

print(bnt_all_char)


```

## Omicron period - Symptomatic Infection 
### Table of characteristic:

```{r echo=FALSE, results='asis'}

library(knitr)
library(gtsummary)


omic = bnt %>% filter(VOC == "Omicron") 

#Table Characteristic for the omicron group 
omic = omic %>% select(id_vigvac,confirmado,idade,sexo,raca,
                       q_measure_1f_12,nome_grande_regiao,outcome,n_comorb, prev_infect, gestante, puerpera,hosp_event,death_event)
omic_char = omic %>% tbl_summary(by = confirmado, include = -id_vigvac, digits = all_categorical() ~ c(0, 1))

print(omic_char)

```

## Omicron period - Symptomatic Infection 
### Number of test positives and test negatives:

```{r echo=FALSE, results='asis'}

library(knitr)
library(gtsummary)


omic = bnt %>% filter(VOC = "Omicron") 

#Table Characteristic for the omicron group 
omic = omic %>% select(id_vigvac,confirmado, status_waning)
omic_char = omic %>% tbl_summary(by = confirmado, include = -id_vigvac, percent = "row",digits = all_categorical() ~ c(0, 2))

print(omic_char)

```

## Omicron period - Symptomatic Infection 
### ODDS RATIO 

```{r echo=FALSE, results='asis'}
library(knitr)
library(parameters)


omic = bnt %>% filter(VOC=="Omicron")

#Model for Symptomatic infection

##Odd Ration - crude
omic_crude = glm(confirmado == "Confirmado" ~ status_waning,
               family = binomial, data = omic)
omic_crude_results = model_parameters(
  omic_crude, exponentiate = T, ci_method="wald")

VE = (1-omic_crude_results$Coefficient)*100
high = (1-omic_crude_results$CI_low)*100
low = (1-omic_crude_results$CI_high)*100

omic_crude_results$VE= VE
omic_crude_results$high = high
omic_crude_results$low = low

kable(omic_crude_results[1:24,], caption = "Odds Ratio - Crude - Symptomatic Infection - omicron",digits = 2)
  
##Odd Ratio - Adjusted 

omic_adj = glm(confirmado == "Confirmado"~status_waning+SE+sexo+idade+raca+q_measure_1f_12+n_comorb+prev_infect+gestante+puerpera+nome_grande_regiao,family = binomial, data = omic)

omic_adj_results = model_parameters(
  omic_adj, exponentiate = T, ci_method="wald") 

VE = (1-omic_adj_results$Coefficient)*100
high = (1-omic_adj_results$CI_low)*100
low = (1-omic_adj_results$CI_high)*100

omic_adj_results$VE= VE
omic_adj_results$high = high
omic_adj_results$low = low

kable(omic_adj_results[1:24,], caption = "Odds Ratio - Adjusted - Symptomatic Infection - Omicron", digits = 2)

```

## Omicron period - Severe outcomes (hospitalisation or death)
### Table of characteristic 


```{r echo=FALSE, results='asis'}
library(knitr)
library(gtsummary)

omic = bnt %>% filter(VOC == "Omicron")

#Severe outcomes 
omic_neg = omic %>% filter(confirmado == "Negativo")
omic_posit = omic %>% filter(confirmado=="Confirmado" & outcome == "Hosp_Death")
omicsev=bind_rows.(omic_neg,omic_posit)

##Table of characteristic from this group 
omicsev = omicsev %>% select(id_vigvac,confirmado,idade,sexo,raca,
                         q_measure_1f_12,nome_grande_regiao,outcome,n_comorb, prev_infect,gestante,puerpera)
omicsev_char = omicsev %>% tbl_summary(by = confirmado, include = -id_vigvac, digits = all_categorical() ~ c(0, 1))

print(omicsev_char)

```

## Omicron period - Severe outcomes (hospitalisation or death)
### Number of test postives and test negatives


```{r echo=FALSE, results='asis'}
library(knitr)
library(gtsummary)

omic = bnt %>% filter(VOC == "Omicron")

#Severe outcomes 
omic_neg = omic %>% filter(confirmado == "Negativo")
omic_posit = omic %>% filter(confirmado=="Confirmado" & outcome == "Hosp_Death")
omicsev=bind_rows.(omic_neg,omic_posit)

##Table of characteristic from this group 
omicsev = omicsev %>% select(confirmado,status_waning)
omicsev_char = omicsev %>% tbl_summary(by = confirmado,  percent = "row", digits = all_categorical() ~ c(0, 2))

print(omicsev_char)

```

## Omicron period - Severe outcomes (hospitalisation or death)
### ODDS RATIO

```{r echo=FALSE, results='asis'}
library(knitr)
library(parameters)

omic = bnt %>% filter(VOC == "Omicron") 

#Severe outcomes 
omic_neg = omic %>% filter(confirmado == "Negativo")
omic_posit = omic %>% filter(confirmado=="Confirmado" & outcome == "Hosp_Death")
omicsev=bind_rows.(omic_neg,omic_posit)



##Odd Ratio - crude
omicsev_crude = glm(confirmado == "Confirmado" ~ status_waning,
                 family = binomial, data = omicsev)
omicsev_crude_results = model_parameters(
  omicsev_crude, exponentiate = T, ci_method="wald")

VE = (1-omicsev_crude_results$Coefficient)*100
high = (1-omicsev_crude_results$CI_low)*100
low = (1-omicsev_crude_results$CI_high)*100

omicsev_crude_results$VE= VE
omicsev_crude_results$high = high
omicsev_crude_results$low = low



kable(omicsev_crude_results[1:24,], caption = "Odds Ratio - Crude - Severe Outcomes - Omicron", digits = 2,format.args = list(scientific = FALSE))


##Odd Ratio - Adjusted 
omicsev_adj = glm(confirmado == "Confirmado" ~ status_waning+SE+sexo+idade+raca+q_measure_1f_12+n_comorb+prev_infect+gestante+puerpera+nome_grande_regiao,
               family = binomial, data = omicsev)
omicsev_adj_results = model_parameters(
  omicsev_adj, exponentiate = T, ci_method="wald")

VE = (1-omicsev_adj_results$Coefficient)*100
high = (1-omicsev_adj_results$CI_low)*100
low = (1-omicsev_adj_results$CI_high)*100

omicsev_adj_results$VE= VE
omicsev_adj_results$high = high
omicsev_adj_results$low = low

kable(omicsev_adj_results[1:24,], caption = "Odds Ratio - Adjusted - Severe Outcomes - Omicron", digits = 2, format.args = list(scientific = FALSE))


```

## Delta period - Symptomatic Infection 
### Table of characteristic:

```{r echo=FALSE, results='asis'}

library(knitr)
library(gtsummary)


delta = bnt %>% filter(VOC == "Delta") 

#Table Characteristic for the omicron group 
delta = delta %>% select(id_vigvac,confirmado,idade,sexo,raca,
                       q_measure_1f_12,nome_grande_regiao,outcome,n_comorb, prev_infect, gestante, puerpera,hosp_event,death_event)
delta_char = delta %>% tbl_summary(by = confirmado, include = -id_vigvac, digits = all_categorical() ~ c(0, 1))

print(delta_char)

```

## omic period - Symptomatic Infection 
### Number of test positives and test negatives:

```{r echo=FALSE, results='asis'}

library(knitr)
library(gtsummary)


delta = bnt %>% filter(VOC == "Delta") 

#Table Characteristic for the omicron group 
delta = delta %>% select(id_vigvac,confirmado, status_waning)
delta_char = delta %>% tbl_summary(by = confirmado, include = -id_vigvac, percent = "row",digits = all_categorical() ~ c(0, 2))

print(delta_char)

```

## omicron period - Symptomatic Infection 
### ODDS RATIO 

```{r echo=FALSE, results='asis'}
library(knitr)
library(parameters)


delta = bnt %>% filter(VOC=="Delta")

#Model for Symptomatic infection

##Odd Ration - crude
delta_crude = glm(confirmado == "Confirmado" ~ status_waning,
               family = binomial, data = delta)
delta_crude_results = model_parameters(
  delta_crude, exponentiate = T, ci_method="wald")

VE = (1-delta_crude_results$Coefficient)*100
high = (1-delta_crude_results$CI_low)*100
low = (1-delta_crude_results$CI_high)*100

delta_crude_results$VE= VE
delta_crude_results$high = high
delta_crude_results$low = low

kable(delta_crude_results[1:12,], caption = "Odds Ratio - Crude - Symptomatic Infection - Delta",digits = 2)
  
##Odd Ratio - Adjusted 

omic_adj = glm(confirmado == "Confirmado"~status_waning+SE+sexo+idade+raca+q_measure_1f_12+n_comorb+prev_infect+gestante+puerpera+nome_grande_regiao,family = binomial, data = delta)

delta_adj_results = model_parameters(
  omic_adj, exponentiate = T, ci_method="wald") 

VE = (1-delta_adj_results$Coefficient)*100
high = (1-delta_adj_results$CI_low)*100
low = (1-delta_adj_results$CI_high)*100

delta_adj_results$VE= VE
delta_adj_results$high = high
delta_adj_results$low = low

kable(delta_adj_results[1:12,], caption = "Odds Ratio - Adjusted - Symptomatic Infection - Delta", digits = 2)

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
