---
title: "Duration Booster - CoronaVac"
author: "Thiago"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3.0
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.width = 8, fig.height = 5)
pacman::p_load(tidyverse, tidylog, mgcv, tidytable,lubridate,gtsummary,survival, showtext, gt, kableExtra,ggh4x,janitor)
source("funs.R")
theme_set(theme_light())
tnd_cv <- read_rds("tnd_cv_1804.RDS")
tnd_cv_pcr <- tnd_cv |> filter(tipo_teste=="RT-PCR")
tnd_cv_ag <- tnd_cv |> filter(tipo_teste=="Antígeno")
tnd_cv_or <- tnd_cv %>% filter(vs_type2 != "uv") %>% mutate(vs_type2 = fct_relevel(vs_type2,"CV_v2_181")) %>% droplevels()
theme_gtsummary_compact()
theme_gtsummary_journal(journal = "nejm")

# Create subset for sensitivity (delay records)
tnd_cv0803 <- tnd_cv |> filter(dt_coleta_valid<"2022-03-08")

```


```{r}
#set theme
theme_Publication <- function(base_size = 14, base_family = "sans") {
  library(grid)
  library(ggthemes)
  (theme_foundation(base_size = base_size, base_family = base_family)
  + theme(
      plot.title = element_text(
        face = "plain",
        size = rel(1.1), hjust = 0.5, margin = margin(0, 0, 20, 0)
      ),
      text = element_text(),
      panel.background = element_rect(colour = NA),
      panel.border = element_rect(colour = NA),
      axis.title = element_text(face = "bold", size = rel(0.8)),
      axis.title.y = element_text(angle = 90, vjust = 2),
      axis.title.x = element_text(vjust = -0.2),
      axis.text = element_text(),
      axis.text.x = element_text(
        color = "black", face = "plain", size = 8,
        margin = margin(t = 6)
      ),
      axis.line.x = element_line(color = "black", size = 1),
      axis.ticks.x = element_line(color = "black", size = 1.5),
      axis.line.y = element_line(colour = "black"),
      axis.ticks = element_line(),
      panel.grid.major = element_line(colour = "#f0f0f0"),
      panel.grid.major.y = element_line(color = "grey90", size = .6),
      plot.background = element_rect(fill = "white", color = "white"),
      panel.grid.minor = element_blank(),
      legend.key = element_rect(colour = NA),
      legend.position = "bottom",
      legend.direction = "horizontal",
      legend.box = "vetical",
      legend.key.size = unit(0.5, "cm"),
      # legend.margin = unit(0, "cm"),
      legend.title = element_text(face = "plain", size = rel(0.8)),
      plot.margin = unit(c(10, 5, 5, 5), "mm"),
      strip.background = element_rect(colour = "#f0f0f0", fill = "#f0f0f0"),
      strip.text = element_text(colour = "black")
    ))
}


tnd_cv %>%
    mutate(vacc_type = case_when(
    str_detect(vs_type2, "^Ad26") ~ "Ad26",
    str_detect(vs_type2, "^CV") ~ "CoronaVac",
    str_detect(vs_type2, "^AZ") ~ "ChAdOx1",
    str_detect(vs_type2, "^BNT162b2") ~ "BNT162b2",
    str_detect(vs_type2, "uv") ~ "Unvaccinated"
  )) |> 
  ggplot(aes(dt_coleta_valid, fill = vacc_type)) +
  geom_histogram(binwidth = 7, color = "white", alpha = 0.7, size = 0.25) +
  labs(y = "No. Individuals", x = "Sample collection date", fill = "") +
  scale_fill_manual(values = c("CoronaVac" = "forestgreen","Unvaccinated"= "firebrick")) +
  scale_y_continuous(labels = scales::comma, limits = c(0, 3.5e5), breaks = seq(0, 3.5e5, .5e5)) +
  scale_x_date(date_breaks = "1 month", date_labels = "%b\n%Y", limits = c(as.Date("2021-12-31"),as.Date("2022-05-01")))+
  theme(legend.position = "bottom") +
  theme_Publication() +
  theme(legend.position = "bottom", panel.spacing.x = unit(1, "lines")) +
  facet_wrap(~confirmado, labeller = as_labeller(c("Negativo" = "Controls", "Confirmado" = "Cases")))


# create plot of variants
path <- "gisaid_variants_statistics_2022_05_05_0658.xlsx"
path %>%
  readxl::excel_sheets() %>%
  set_names() %>%
  map_df(~ readxl::read_excel(path = path, sheet = .x), .id = "sheet") %>%
  janitor::clean_names() %>%
  fill(x1, .direction = "down") %>%
  filter(!is.na(x1)) %>%
  mutate(count_total = coalesce(!!!select(., starts_with("voc")))) %>%
  relocate(count_total, .after = x1) %>%
  select(!matches("^voc|^voi"), -readme_variants_download_package) %>%
  pivot_longer(cols = -c(sheet:count_total), names_to = "date", values_to = "value") %>%
  filter(x1 == "Brazil", !is.na(count_total)) %>%
  pivot_wider(names_from = count_total, values_from = value) %>%
  filter(!is.na(count)) %>%
  mutate(
    date = str_remove(date, "^x"),
    date = lubridate::ymd(date)
  ) %>%
  pivot_wider(names_from = sheet, values_from = count) %>%
  mutate(across(3:last_col(), ~ .x * 100 / total)) %>%
  select(-x1) |>
  janitor::clean_names() %>%
  select(-voc_beta) |>
  mutate(voc_wt = 100 - rowSums(across(voc_omicron:voc_gamma), na.rm = T)) |>
  arrange(date) |>
  select(-total) %>%
  pivot_longer(names_to = "voc", values_to = "pct", cols = voc_omicron:voc_wt) |>
  filter(date > "2021-01-18") |>
  ggplot(aes(date, pct, fill = voc)) +
  labs(x="Date",y="Relative Frequency %",fill="Variant")+
  geom_area(color = "white", position = "stack", size = 0.5, alpha = 0.7) +
  scale_x_date(breaks = "1 month", date_labels = "%b\n%Y", limits = c(NA_Date_, as.Date("2022-05-01"))) +
  scale_fill_discrete(labels=c("Alpha","Delta","Gamma","Omicron","Non-VOC/VOI"))+
  theme_Publication()

```


# TND Tables

## Overall

```{r tnd_tables}
tnd_cv %>%
    mutate(vacc_type = case_when(
    str_detect(vs_type2, "^Ad26") ~ "Ad26",
    str_detect(vs_type2, "^CV") ~ "CoronaVac",
    str_detect(vs_type2, "^AZ") ~ "ChAdOx1",
    str_detect(vs_type2, "^BNT162b2") ~ "BNT162b2",
    str_detect(vs_type2, "uv") ~ "Unvaccinated"
  )) %>%
  select(
    idade, sexo, raca,age_group, capital_not, tipo_teste,
    q_measure_1f_12,diabetes,obesidade, imunossupressao, drespiratoria, dcardiaca,
    drc, n_comorb_cat, prev_infec, confirmado, diff1_2,diff2_3,hosp_event,
    death_event, outcome, vacc_type,  id_vigvac,vs_type2
  ) %>%
  mutate(
    hosp_event = fct_explicit_na(hosp_event),
    death_event = fct_explicit_na(death_event),
    third_dose = str_detect(vs_type2,"v3"),
    q_measure_1f_12 = fct_explicit_na(q_measure_1f_12)
  ) %>%
  mutate.(individuals=row_number.(),.by=id_vigvac) %>%
  mutate(confirmado=fct_recode(confirmado,
                               "Positive"= "Confirmado",
                               "Negative"= "Negativo")) %>%
  relocate(individuals, .before=idade) %>%
  tbl_summary(
          by = confirmado,
          include = -id_vigvac,
          digits = list(all_categorical() ~ c(0, 1)),
          label = list(
            individuals ~ "Individuals",
            idade ~ "Age",
            q_measure_1f_12 ~ "Deprivation Index",
            sexo ~ "Sex-Female",
            confirmado ~ "Test Result",
            raca ~ "Race",
            capital_not ~ "Residence in capital",
            tipo_teste ~ "Test type",
            diabetes ~ "Diabetes",
            obesidade ~ "Obesity",
            imunossupressao ~ "Immunosuppression",
            drespiratoria ~ "Chronic respiratory disease",
            dcardiaca ~ "Cardiac disease",
            drc ~ "Chronic Kidney Disease",
            n_comorb_cat ~ "No. comorbidities",
            prev_infec ~ "Previously infected",
            hosp_event ~ "Hospitalization",
            death_event ~ "Death",
            outcome ~ "Severe outcome",
            diff1_2 ~ "Interval 1st 2nd",
            diff2_3 ~ "Interval 2nd 3rd"
          ),
          value = list(
            sexo ~ "F",
            individuals ~ "1",
            capital_not ~ "Capital",
            outcome ~ "Hosp_Death",
            death_event ~ "Death-related",
            hosp_event ~ "Hospitalization"
        )) %>%
        bold_labels()



tnd_cv %>%
    mutate(vacc_type = case_when(
    str_detect(vs_type2, "^Ad26") ~ "Ad26",
    str_detect(vs_type2, "^CV") ~ "CoronaVac",
    str_detect(vs_type2, "^AZ") ~ "ChAdOx1",
    str_detect(vs_type2, "^BNT162b2") ~ "BNT162b2",
    str_detect(vs_type2, "uv") ~ "Unvaccinated"
  )) %>%
  select(
    idade, sexo, raca,age_group, capital_not, tipo_teste,
    q_measure_1f_12,diabetes,obesidade, imunossupressao, drespiratoria, dcardiaca,
    drc, n_comorb_cat, prev_infec, confirmado, diff1_2,diff2_3,hosp_event,
    death_event, outcome, vacc_type,  id_vigvac,vs_type2
  ) %>%
  mutate(
    hosp_event = fct_explicit_na(hosp_event),
    death_event = fct_explicit_na(death_event),
    third_dose = str_detect(vs_type2,"v3"),
    q_measure_1f_12 = fct_explicit_na(q_measure_1f_12)
  ) %>%
  mutate.(individuals=row_number.(),.by=id_vigvac) %>%
  mutate(confirmado=fct_recode(confirmado,
                               "Positive"= "Confirmado",
                               "Negative"= "Negativo")) %>%
  relocate(individuals, .before=idade) %>%
  tbl_summary(
          by = vacc_type,
          include = -id_vigvac,
          digits = list(all_categorical() ~ c(0, 1)),
          label = list(
            individuals ~ "Individuals",
            idade ~ "Age",
            q_measure_1f_12 ~ "Deprivation Index",
            sexo ~ "Sex-Female",
            confirmado ~ "Test Result",
            raca ~ "Race",
            capital_not ~ "Residence in capital",
            tipo_teste ~ "Test type",
            diabetes ~ "Diabetes",
            obesidade ~ "Obesity",
            imunossupressao ~ "Immunosuppression",
            drespiratoria ~ "Chronic respiratory disease",
            dcardiaca ~ "Cardiac disease",
            drc ~ "Chronic Kidney Disease",
            n_comorb_cat ~ "No. comorbidities",
            prev_infec ~ "Previously infected",
            hosp_event ~ "Hospitalization",
            death_event ~ "Death",
            outcome ~ "Severe outcome",
            diff1_2 ~ "Interval 1st 2nd",
            diff2_3 ~ "Interval 2nd 3rd"
          ),
          value = list(
            sexo ~ "F",
            individuals ~ "1",
            capital_not ~ "Capital",
            outcome ~ "Hosp_Death",
            death_event ~ "Death-related",
            hosp_event ~ "Hospitalization"
        )) %>%
        bold_labels()
```

\
\

```{r tnd_tables2}
tnd_cv %>%
    mutate(vacc_type = case_when(
    str_detect(vs_type2, "^Ad26") ~ "Ad26",
    str_detect(vs_type2, "^CV") ~ "CoronaVac",
    str_detect(vs_type2, "^AZ") ~ "ChAdOx1",
    str_detect(vs_type2, "^BNT162b2") ~ "BNT162b2",
    str_detect(vs_type2, "uv") ~ "Unvaccinated"
  )) %>%
  select(
    idade, sexo, raca,age_group, capital_not, tipo_teste,
    q_measure_1f_12,diabetes,obesidade, imunossupressao, drespiratoria, dcardiaca,
    drc, n_comorb_cat, prev_infec, confirmado, diff1_2,diff2_3,hosp_event,
    death_event, outcome, vacc_type,  id_vigvac,vs_type2,vacc_type
  ) %>%
  mutate(
    hosp_event = fct_explicit_na(hosp_event),
    death_event = fct_explicit_na(death_event),
    q_measure_1f_12 = fct_explicit_na(q_measure_1f_12)
  ) %>%
  mutate.(individuals=row_number.(),.by=id_vigvac) %>%
  mutate(confirmado=fct_recode(confirmado,
                               "Positive"= "Confirmado",
                               "Negative"= "Negativo")) %>%
  relocate(individuals, .before=idade) %>%
  tbl_strata(
    strata = vacc_type,
    .tbl_fun =
      ~ .x %>%
        tbl_summary(
          by = confirmado,
          include = -id_vigvac,
          digits = list(all_categorical() ~ c(0, 1)),
          label = list(
            individuals ~ "Individuals",
            idade ~ "Age",
            q_measure_1f_12 ~ "Deprivation Index",
            sexo ~ "Sex-Female",
            raca ~ "Race",
            capital_not ~ "Residence in capital",
            tipo_teste ~ "Test type",
            diabetes ~ "Diabetes",
            obesidade ~ "Obesity",
            imunossupressao ~ "Immunosuppression",
            drespiratoria ~ "Chronic respiratory disease",
            dcardiaca ~ "Cardiac disease",
            drc ~ "Chronic Kidney Disease",
            n_comorb_cat ~ "No. comorbidities",
            prev_infec ~ "Previously infected",
            hosp_event ~ "Hospitalization",
            death_event ~ "Death",
            outcome ~ "Severe outcome",
            diff1_2 ~ "Interval 1st 2nd",
            diff2_3 ~ "Interval 2nd 3rd"
          ),
          value = list(
            sexo ~ "F",
            individuals ~ "1",
            capital_not ~ "Capital",
            outcome ~ "Hosp_Death",
            death_event ~ "Death-related",
            hosp_event ~ "Hospitalization"
          )
        ) %>%
        bold_labels()
  )
```

\

## TND - CoronaVac - Age Group

```{r tnd_tables_az}
tnd_cv %>%
  mutate(
    outcome_confirmado = fct_recode(outcome_confirmado,
      "Severe Pos" = "Hosp_Death_Positive"
    ),
    outcome_confirmado = fct_relevel(
      outcome_confirmado,
      "Negative",
      "Outpatient_Positive",
      "Severe Pos"
    )
  )%>%
  droplevels() %>%
  select(vs_type2, outcome_confirmado, age_group) %>%
  mutate(vs_type2 = fct_relevel(
    factor(vs_type2),
    "uv",
      "CV_v1_0:1",
      "CV_v1_2",
      "CV_v2_0:13",
      "CV_v2_14:180",
      "CV_v2_181",
      "CV_v3_0:13_BNT162b2",
      "CV_v3_14:30_BNT162b2",
      "CV_v3_31:60_BNT162b2",
      "CV_v3_61:90_BNT162b2",
      "CV_v3_91:120_BNT162b2",
      "CV_v3_121_BNT162b2",
      "CV_v3_0:13_CV",
      "CV_v3_14:30_CV",
      "CV_v3_31:60_CV",
      "CV_v3_61:90_CV",
      "CV_v3_91:120_CV",
      "CV_v3_121_CV"
  )) %>%
  tbl_strata(
    strata = age_group,
    .tbl_fun =
      ~ .x %>% tbl_summary(
        by = outcome_confirmado,
        percent = "row",
        label = list(
          vs_type2 = "Vaccination Status",
          voc = "VOC"
        ),
        digits = list(all_categorical() ~ c(0, 1))
      ),
    .combine_with = "tbl_stack"
  ) %>% bold_labels() %>% as_gt %>% tab_options(table.width=pct(50))


tnd_cv %>%
  mutate(
    outcome_confirmado = fct_recode(outcome_confirmado,
      "Severe Pos" = "Hosp_Death_Positive"
    ),
    outcome_confirmado = fct_relevel(
      outcome_confirmado,
      "Negative",
      "Outpatient_Positive",
      "Severe Pos"
    )
  )%>%
  droplevels() %>%
  select(vs_type2, outcome_confirmado, age_group) %>%
  mutate(vs_type2 = fct_relevel(
    factor(vs_type2),
    "uv",
      "CV_v1_0:1",
      "CV_v1_2",
      "CV_v2_0:13",
      "CV_v2_14:180",
      "CV_v2_181",
      "CV_v3_0:13_BNT162b2",
      "CV_v3_14:30_BNT162b2",
      "CV_v3_31:60_BNT162b2",
      "CV_v3_61:90_BNT162b2",
      "CV_v3_91:120_BNT162b2",
      "CV_v3_121_BNT162b2",
      "CV_v3_0:13_CV",
      "CV_v3_14:30_CV",
      "CV_v3_31:60_CV",
      "CV_v3_61:90_CV",
      "CV_v3_91:120_CV",
      "CV_v3_121_CV"
  )) %>%
 tbl_summary(
        by = outcome_confirmado,
        percent = "row",
        label = list(
          vs_type2 = "Vaccination Status",
          voc = "VOC"
        ),
        digits = list(all_categorical() ~ c(0, 1))
      ) %>% bold_labels() %>% as_gt %>% tab_options(table.width=pct(50))
```


# median iqr >120d
```{r}
tnd_cv |> filter(vacc_status=="v3_121") |> tbl_summary(by=age_group,include=days_vacc_3_test)
```


# plot status by time

```{r}
tnd_cv |> filter(vs_type!="uv", str_detect(vs_type,"v3")) |> ggplot(aes(dt_coleta_valid,fill=vs_type))+geom_histogram(binwidth =7, color="white")+facet_wrap(~age_group)+ scale_x_date(date_breaks = "1 month", date_labels = "%b\n%Y", limits = c(as.Date("2021-12-31"),NA))
```


# tipo teste por faixa etaria
```{r}
tnd_cv |> tbl_summary(by=age_group,include=tipo_teste)
```


# VE

## Infection

```{r}
infection <- models_fit(tnd_cv)
infection_age<- tnd_cv %>% nest(data=!age_group) %>%  mutate(fit = map(data,models_fit))
fun_table_ve(infection,infection_age,"Infection-Symptomatic")
fun_plot_ve_type(infection,infection_age)

```

## Infection using only rt-pcr

```{r}
infection <- models_fit(tnd_cv_pcr)
infection_age<- tnd_cv_pcr %>% nest(data=!age_group) %>%  mutate(fit = map(data,models_fit))
fun_table_ve(infection,infection_age,"Infection-Symptomatic")
fun_plot_ve_type(infection,infection_age)

```

## Infection using only ag

```{r}
infection <- models_fit(tnd_cv_ag)
infection_age<- tnd_cv_ag %>% nest(data=!age_group) %>%  mutate(fit = map(data,models_fit))
fun_table_ve(infection,infection_age,"Infection-Symptomatic")
fun_plot_ve_type(infection,infection_age)

```




## Severe outcomes

```{r}
severe_db <- tnd_cv %>% filter(outcome_confirmado != "Outpatient_Positive")
severe <- models_fit(severe_db)
severe_age<- severe_db %>% nest(data=!age_group) %>%  mutate(fit = map(data,models_fit))
fun_table_ve(severe,severe_age,"Severe")
fun_plot_ve_type(severe,severe_age)
```


## Severe outcomes using only rt-pcr

```{r}
severe_db <- tnd_cv_pcr %>% filter(outcome_confirmado != "Outpatient_Positive")
severe <- models_fit(severe_db)
severe_age<- severe_db %>% nest(data=!age_group) %>%  mutate(fit = map(data,models_fit))
fun_table_ve(severe,severe_age,"Severe")
fun_plot_ve_type(severe,severe_age)
```

## Severe outcomes using only lateral-flow

```{r}
severe_db <- tnd_cv_ag %>% filter(outcome_confirmado != "Outpatient_Positive")
severe <- models_fit(severe_db)
severe_age<- severe_db %>% nest(data=!age_group) %>%  mutate(fit = map(data,models_fit))
fun_table_ve(severe,severe_age,"Severe")
fun_plot_ve_type(severe,severe_age)
```



## Plot combined

```{r}
severe_db <- tnd_cv %>% filter(outcome_confirmado != "Outpatient_Positive")
severe <- models_fit(severe_db)
severe_age<- severe_db %>% nest(data=!age_group) %>%  mutate(fit = map(data,models_fit))
infection <- models_fit(tnd_cv)
infection_age<- tnd_cv %>% nest(data=!age_group) %>%  mutate(fit = map(data,models_fit))

df_plot <- infection %>%
  mutate(model = "Symptomatic COVID-19") |>
  bind_rows(infection_age %>% select(fit) %>% unnest(names_repair = "check_unique", cols = c(fit)) |> mutate(model = "Symptomatic COVID-19"), severe |> mutate(model = "Severe COVID-19"), severe_age %>% select(fit) %>% unnest(names_repair = "check_unique", cols = c(fit)) |> mutate(model = "Severe COVID-19")) |>
  filter(str_detect(term, "CV_v3")) |>
  mutate(age_group = case_when(
    str_detect(age_group, "18-124|18-123") ~ "Overall",
    str_detect(age_group, "18-59") ~ "18-59",
    str_detect(age_group, "60-79") ~ "60-79",
    str_detect(age_group, "80-124|80-123") ~ "\u2265 80"
  ), age_group = fct_relevel(factor(age_group), "Overall", "18-59", "60-79")) |>
  mutate(across(or:conf.high, ~ (1 - .x) * 100)) %>%
  mutate(across(or:conf.high, ~ if_else(.x < (-1000) | .x > 1000, Inf, .x))) %>%
  mutate(
    type = case_when(
      str_detect(term, "CV$") ~ "CV-Booster",
      str_detect(term, "BNT162b2$") ~ "BNT162b2-Booster",
      str_detect(term, "BNT162b2$|CV$", negate = T) ~ "No booster"
    ),
    model = fct_relevel(factor(model), "Severe COVID-19")
  ) %>%
  mutate(
    term = str_remove(term, "CV_"),
    term = str_remove(term, "_CV$"),
    term = str_remove(term, "_BNT162b2$")
  ) %>%
  filter(type != "No booster") %>%
  group_by(type, age_group) %>%
  mutate(term = fct_case_when(
    str_detect(term, "v3_0:13") ~ "0-13",
    str_detect(term, "v3_14:30") ~ "14-30",
    str_detect(term, "v3_31:60") ~ "31-60",
    str_detect(term, "v3_61:90") ~ "61-90",
    str_detect(term, "v3_91:120") ~ "91-120",
    str_detect(term, "v3_121") ~ ">120"
  )) %>%
  arrange(term, type, age_group)
df_rect <- df_plot %>% summarise(group = unique(age_group))


df_plot |> ggplot(aes(x = term, y = or, ymin = conf.low, ymax = conf.high, color = model)) +
  geom_rect(
    data = df_rect, aes(fill = age_group), inherit.aes = FALSE,
    xmin = -Inf, xmax = Inf,
    ymin = -Inf, ymax = Inf
  ) +
  scale_fill_manual(values = alpha(c("white", "gray85", "white", "gray85"), 0.3)) +
  guides(
    fill = "none",
    color = guide_legend(override.aes = list(linetype = 1))
  ) +
  geom_hline(yintercept = 0, lty = 2, size = 0.1) +
  geom_pointrange(shape = 1, size = 0.9, stroke = 0.4, position = position_jitterdodge(dodge.width = 1)) +
  labs(y = "Vaccine Effectiveness (%)", x = "Days since BNT162b2 Booster", title = "", color = "Outcome:") +
  scale_y_continuous(breaks = c(-10, 0, 20, 40, 60, 80, 100), expand = c(0, 0)) +
  facet_nested(~age_group, labeller = as_labeller(
    c(
      "Overall" = "Overall",
      "18-59" = "18-59 years",
      "60-79" = "60-79 years",
      "\u2265 80" = "\u2265 80 years"
    )
  )) +
  theme(axis.text.x = element_text(angle = 0)) +
  theme(strip.background = element_rect(fill = "white")) +
  theme(
    strip.text = element_text(colour = "black", face = "bold"),
    # axis.line.x = element_line(color = "black", size = 0.5),
    axis.text.x = element_text(
      color = "black", face = "plain", size = 8,
      margin = margin(t = 6)
    ),
    panel.spacing.x = unit(0.0, "lines"),
    axis.text.y = element_text(
      color = "black", face = "plain"
    ),
    panel.spacing.y = unit(1, "lines"),
    axis.title.x = element_text(margin = unit(c(3, 0, 0, 0), "mm")),
    legend.position = "bottom"
  ) +
  coord_cartesian(ylim = c(-10, 100))


```


## Death

```{r}
severe_db <- tnd_cv %>%  filter((death_event == "Death-related" & confirmado == "Confirmado") | confirmado == "Negativo")
severe <- models_fit(severe_db)
severe_age<- severe_db %>% nest(data=!age_group) %>%  mutate(fit = map(data,models_fit))
fun_table_ve(severe,severe_age,"Death")
fun_plot_ve_type(severe,severe_age)
```

## Death only rt-pcr

```{r}
severe_db <- tnd_cv_pcr %>%  filter((death_event == "Death-related" & confirmado == "Confirmado") | confirmado == "Negativo")
severe <- models_fit(severe_db)
severe_age<- severe_db %>% nest(data=!age_group) %>%  mutate(fit = map(data,models_fit))
fun_table_ve(severe,severe_age,"Death")
fun_plot_ve_type(severe,severe_age)
```


## Death only ag

```{r}
severe_db <- tnd_cv_ag %>%  filter((death_event == "Death-related" & confirmado == "Confirmado") | confirmado == "Negativo")
severe <- models_fit(severe_db)
severe_age<- severe_db %>% nest(data=!age_group) %>%  mutate(fit = map(data,models_fit))
fun_table_ve(severe,severe_age,"Death")
fun_plot_ve_type(severe,severe_age)
```


# OR

Compared to Coronavac 181+ days

## Infection

```{r}
infection <- models_fit(tnd_cv_or)
infection_age<- tnd_cv_or %>% nest(data=!age_group) %>%  mutate(fit = map(data,models_fit))
fun_table_or(infection,infection_age,"Infection-Symptomatic")
fun_plot_or_type(infection,infection_age)
```

## Severe outcomes

```{r}
severe_db <- tnd_cv_or %>% filter(outcome_confirmado != "Outpatient_Positive")
severe <- models_fit(severe_db)
severe_age<- severe_db %>% nest(data=!age_group) %>%  mutate(fit = map(data,models_fit))
fun_table_or(severe,severe_age,"Severe")
fun_plot_or_type(severe,severe_age)
```


# Plot combined

```{r}
infection %>% mutate(model="Symptomatic COVID-19") |>  bind_rows(infection_age %>%  select(fit) %>% unnest(names_repair = "check_unique",cols = c(fit)) |> mutate(model="Symptomatic COVID-19"),severe |> mutate(model="Severe COVID-19"),severe_age %>%  select(fit) %>% unnest(names_repair = "check_unique",cols = c(fit)) |> mutate(model="Severe COVID-19")) |> filter(str_detect(term,"CV_v3")) |>
  mutate(age_group=case_when(
  str_detect(age_group,"18-121|18-123")~"Overall",
  str_detect(age_group,"18-59")~"18-59",
  str_detect(age_group,"60-79")~"60-79",
  str_detect(age_group,"80-121|80-123")~"\u2265 80"
), age_group=fct_relevel(factor(age_group),"Overall","18-59","60-79")) |> 
    mutate(type = case_when(
      str_detect(term, "CV$") ~ "CV-Booster",
      str_detect(term, "BNT162b2$") ~ "BNT162b2-Booster",
      str_detect(term, "BNT162b2$|CV$", negate = T) ~ "No booster"
    ),
    model=fct_relevel(factor(model),"Severe COVID-19")) %>%
    mutate(
      term = str_remove(term, "CV_"),
      term = str_remove(term, "_CV$"),
      term = str_remove(term, "_BNT162b2$")
    ) %>% filter(type != "No booster") %>% 
    group_by(type, age_group) %>%
    mutate(term = fct_case_when(
      str_detect(term,"v3_0:13")~ "0-13",
      str_detect(term,"v3_14:30")~ "14-30",
      str_detect(term,"v3_31:60")~ "31-60",
      str_detect(term,"v3_61:90")~ "61-90",
      str_detect(term,"v3_91:120")~ "91-120",
      str_detect(term,"v3_121")~ ">120"
    )) %>%
    arrange(term, type, age_group) %>% 
    ggplot(aes(x = term, y = or, ymin = conf.low, ymax = conf.high, color=model)) +
    geom_hline(yintercept = 1, lty=2,size=0.1)+
    geom_pointrange(shape=1, size=0.5, stroke=0.4,position = position_jitterdodge(dodge.width = 0.9)) +
    labs(y = "Odd's Ratio", x = "Days since BNT162b2 Booster", title="", color="Outcome:") +
  scale_y_continuous(breaks = seq(0,1.2,.20),expand = c(0, 0))+
    facet_nested(~age_group) +
    theme(axis.text.x = element_text(angle = 0)) +
    theme(strip.background = element_rect(fill = "gray90")) +
    theme(strip.text = element_text(colour = "black"),
          #axis.line.x = element_line(color = "black", size = 0.5),
          axis.text.x = element_text(
        color = "black", face = "plain", size = 8,
        margin = margin(t = 6)
      ),
      axis.text.y = element_text(
        color = "black", face = "plain"
      ),
      panel.spacing.y= unit(1, "lines"),
      axis.title.x = element_text(margin = unit(c(3, 0, 0, 0), "mm")),
      legend.position = "bottom") +
    coord_cartesian(ylim = c(0, 1.2))
```



## Death

```{r}
severe_db <- tnd_cv_or %>%  filter((death_event == "Death-related" & confirmado == "Confirmado") | confirmado == "Negativo")
severe <- models_fit(severe_db)
severe_age<- severe_db %>% nest(data=!age_group) %>%  mutate(fit = map(data,models_fit))
fun_table_or(severe,severe_age,"Death")
fun_plot_or_type(severe,severe_age)
```


# Sensitivity - delay

## Infection

```{r}
infection <- models_fit(tnd_cv0803)
infection_age<- tnd_cv0803 %>% nest(data=!age_group) %>%  mutate(fit = map(data,models_fit))
fun_table_ve(infection,infection_age,"Infection-Symptomatic")
fun_plot_ve_type(infection,infection_age)
```

## Severe

```{r}
severe_db <- tnd_cv0803 %>% filter(outcome_confirmado != "Outpatient_Positive")
severe <- models_fit(severe_db)
severe_age<- severe_db %>% nest(data=!age_group) %>%  mutate(fit = map(data,models_fit))
fun_table_ve(severe,severe_age,"Severe")
fun_plot_ve_type(severe,severe_age)
```

# Trend Analysis

```{r}
tnd_cv_trend <- tnd_cv |> filter(str_detect(vacc_status,"v3")) |> droplevels()
tnd_cv_trend$vs_type2 <- factor(tnd_cv_trend$vs_type2,ordered = T)
tnd_cv_trend <- tnd_cv_trend |> filter(vs_type2!="CV_v3_0:13_BNT162b2") |> droplevels()
levels(tnd_cv_trend$vs_type2)

trend_fun <- function(data){
mod <- bam(confirmado == "Confirmado" ~ vs_type2 +
    s(temporal_trend, bs = "cr") +
    s(idade, bs = "cr") +
    prev_infec +
    sexo +
    uf +
    diabetes +
    obesidade +
    imunossupressao +
    drespiratoria +
    dcardiaca +
    drc +
    q_measure_1f_12 +
    capital_not,
  family = binomial, nthreads = 24, discrete = T, data = data)
  parameters::model_parameters(mod,ci_method="wald", keep="vs_type2", exponentiate=T)}


trend_inf_age<- tnd_cv_trend %>% nest(data=!age_group) %>%  mutate(fit = map(data,trend_fun))
trend_sev_age<- tnd_cv_trend |> filter(outcome_confirmado!="Outpatient_Positive") %>% nest(data=!age_group) %>%  mutate(fit = map(data,trend_fun))
trend_inf_age |> select(fit, age_group) |> unnest(names_repair = "check_unique",cols = c(fit)) 
trend_sev_age |> select(fit, age_group) |> unnest(names_repair = "check_unique",cols = c(fit)) 
trend_fun(tnd_cv_trend)
trend_fun(tnd_cv_trend|> filter(outcome_confirmado!="Outpatient_Positive")) 

```

